Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-01-29 alloscore_manuscript/alloscore-application-shorter.Rnw
removing Rosa from acknowledgments, per her request and state guidelines.

We wish to thank the following individuals who contributed valuable comments and feedback on early versions of this work: Matthew Biggerstaff, Rebecca Borchering, Rosa Ergas, Sebastian Funk, Melissa Kerr, and Jeffrey Shaman.

>>>>

We wish to thank the following individuals who contributed valuable comments and feedback on early versions of this work: Matthew Biggerstaff, Rebecca Borchering, Sebastian Funk, Melissa Kerr, and Jeffrey Shaman.
